---
title: "p8105_hw1_rq2166"
author: "Ruoyuan Qian"
date: "2019/9/14"
output: github_document
---

# Problem 1

##create data frame
```{r create data frame}
library(tidyverse)
df <- tibble( ran=rnorm(8),
              logic= ran>0,
              char= c("I", "l", "o", 
                             "v","e", "d","s","!"),
              fact=factor(c(rep(1,3),rep(2,4),rep(3,1))))

#calculate means
mean(df$ran)
mean(df$logic)
mean(df$char)
mean(df$fact)
```

##define as numeric
```{r define as numeric, eval=FALSE}
as.numeric(df$logic)
as.numeric(df$char)
as.numeric(df$fact)

```

In problem one, When I try to take the mean of each variable, the logical vector and random vector work, but the charater vector and the factor vector display warnings and get "NA" results.


When I use `as.numeric()` function to change the them into numeric vectors, the logical vector and factor vector work, but sill displaying warnings in charactor vector. 


It dose explain the failure in calculating the mean in charactor and factor vectors, since they are initially defined as charactors, which is impossible to determine the means. That's why there are warnings and "NA"s in them.


##logical vector converting
```{r convert logical vector}
#covert logical vector to numric vetor 
logic_numeric <- as.numeric(df$logic)
 logic_numeric * df$ran

#covert logical vector to factor vetor 
logic_fact <- as.factor(df$logic)
 logic_fact * df$ran

#covert logical vector to factor and then convert result
logic_fact <- as.factor(df$logic)
fact_num <- as.numeric(logic_fact )
 fact_num*df$ran

```

# Problem 2

##create data frame and make description
```{r Problem 2 descript data frame}
library(tidyverse)

df2<-tibble(x=rnorm(500),
            y=rnorm(500),
            logic= x+y>1,
            nume=as.numeric(logic),
            fac=as.factor(logic))


x_sum <- tibble( nrow=nrow(df2),
                 ncol=ncol(df2),
                 x_mean=mean(df2$x),
                 x_median=median(df2$x),
                 x_SD=sd(df2$x) )
x_sum

prop.table(table(df2$logic))

```

##draw plots
```{r Problem 2 draw plot}
library(ggplot2)

ggplot(df2, aes(x, y,color= df2$logic))+geom_point(size = 1.0)+ labs(title="scatterplot of y vs x",x="x",y="y")

ggplot(df2, aes(x, y,color= df2$nume))+geom_point(size = 1.0, shape = 16)+
  labs(title="scatterplot of y vs x",x="x",y="y")
ggplot(df2, aes(x, y,color= df2$fac))+geom_point(size = 1.0, shape = 16)+
  labs(title="scatterplot of y vs x",x="x",y="y")


```

#save plot 1
```{r save plot 1}
plot_1 <- ggplot(df2, aes(x, y,color= df2$logic))+geom_point(size = 1.0)+ labs(title="scatterplot of y vs x",x="x",y="y")
ggsave("plot_1.pdf")
```
The color scales are different based on the different types of variables in `color=`function. 

As for the logical variable, the scale contains just two groups, TRUE and FALSE. 

As for the numeric variable, the scale is a continuous vector from `0` to `1`, TRUE and FALSE. 

As for the logical variable, the scale contains just two groups, TRUE and FALSE, which is same as the first one. 
